For Induction-Induction, Induction is Enough

### 2019-11-11 paper/paper.tex
stuff

\subsection{Infinitary IITs}.

The current work only concerns finitary IITs. An extension would be to also
allow infinitely branching inductive types such as W-types. This would first
require giving semantics for infinitary IITs (to our knowledge there is no
previously published semantics that we can borrow), and also giving a term model
construction analogously to finitary QIITs. These steps seem feasible. However,
it seems to be more difficult to construct the syntax of infinitary IIT
signatures without using quotients. The reason is that such syntax would not be
strictly restricted to neutral terms: we would need $\lambda$-abstraction and
$\beta\eta$-rules for infinitary $\Pi$ types, in order to allow a term model
construction for infinitary IITs. A definition for normal preterms and typing
judgments on them may still be possible, but it appears to be much more
complicated than before (the current authors have attempted this without
conclusive success).

\subsection{Construction without UIP and function extensionality}
\todo{Without UIP, without funext,
for QIITs (in the setoid model).}

>>>>

The current work only concerns finitary IITs. An extension would be to also
allow infinitely branching inductive types such as W-types. This would first
require giving semantics for infinitary IITs (to our knowledge there is no
previously published semantics that we can borrow), and also giving a term model
construction analogously to finitary QIITs. These steps seem feasible. However,
it seems to be more difficult to construct the syntax of infinitary IIT
signatures without using quotients. The reason is that such syntax would not be
strictly restricted to neutral terms: we would need $\lambda$-abstraction and
$\beta\eta$-rules for infinitary $\Pi$ types, in order to allow a term model
construction for infinitary IITs. A definition of normal preterms and typing
judgments on them may still be possible, but it appears to be much more
complicated than before (the current authors have attempted this without
conclusive success).

As mentioned in Section \ref{sec:right_uniqueness}, it also remains an open
problem whether IITs are reducible to inductive types in a UIP-free setting. To
show this, we would need to construct the syntax of signatures without UIP, and
also reproduce the semantics and term model construction for IITs without UIP.
